Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-01 paper_comparison/paper_comparison/paper_comparison.Rmd
cleaned up table 2

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", "NA"),
           sigma = c("0.25", "1", "2", "4", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1", "4", "16", "64"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "cccccc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Summary of factors involved in the study.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "Standard deviation of polynomial model\n(sym3)",
                                 "Shape of heteroskedasticity\n(sym4)", 
                                 "Variance factor of heteroskedasticity model\n(sym5)",
                                 "Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

>>>>

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", "NA"),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rcrrrr",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Description of all factors involved in the nonlinear and heteroskedasticity studies.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Poly Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Heteroskedasticity (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)")) %>% #"Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

### 2022-12-01 paper_comparison/paper_comparison/paper_comparison.tex
cleaned up table 2

\caption{\label{tab:model-factor-table}Summary of factors involved in the study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{1}{c}{\makecell[c]{Order of Hermite polynomial\\($j$)}} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{\makecell[c]{Standard deviation of polynomial model\\($\sigma$)}} & \multicolumn{1}{c}{\makecell[c]{Shape of heteroskedasticity\\($a$)}} & \multicolumn{1}{c}{\makecell[c]{Variance factor of heteroskedasticity model\\($b$)}} & \multicolumn{1}{c}{\makecell[c]{Sample size\\($n$)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1 & 0 & 1 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2 & 1 & 4 & 300\\
18 & $U\{1, 5\}$ & 4 &  & 16 & \\
 & NA &  &  & 64 & \\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:model-factor-table}Description of all factors involved in the nonlinear and heteroskedasticity studies.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rcrrrr}
\toprule
\multicolumn{1}{c}{Poly Order ($j$)} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{SD ($\sigma$)} & \multicolumn{1}{c}{Poly Shape ($a$)} & \multicolumn{1}{c}{Heteroskedasticity ($b$)} & \multicolumn{1}{c}{Size ($n$)} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1.00 & 0 & 1.00 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2.00 & 1 & 4.00 & 300\\
18 & $U\{1, 5\}$ & 4.00 &  & 16.00 & \\
 & NA &  &  & 64.00 & \\
\bottomrule
\end{tabular}}
\end{table}
